Temperature Effects on Surface Sulfur Dioxide

### 2011-08-26 Coordination-Results.tex
New round of edits given out to others

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/so2-coordinations-percents-small.png}
		\caption{The \suldiox~bonding coordinations occur with different frequencies at the surface under hot and cold temperature conditions. Shown above is the distribution of bonding coordinations of the cold (blue) and hot (red) \suldiox~over the entire set of trajectories. The values are the percentage of MD timesteps spent in the given bonding coordintion.}
		\label{fig:bonding-coordinations}
	\end{center}
\end{figure}

	Several conclusions about the bonding behavior of \suldiox~to surface waters stem from this distribution of coordinations. Clearly the cold \suldiox~spends more time than the hot \suldiox, 13\% versus 3\%, respectively, completely unbound from the surface waters. This does not necessarily imply a complete desorption into the gas phase, but only a brief sojourn away from the waters, with all interactions and bond lengths longer than the cutoff criteria used for the analysis. Furthermore, the most frequently occuring bonding coordinations are ``S'',``SO'', and ``SOO'', with ``SO'' being the most populated at both temperatures. Baer et al. also concluded that these three coordinations were the most frequent for a room temperature simulation, and specifically identified the ``SO'' and ``SOO'' as most common in their study.\cite{Baer2010}

@@

% Baer's assymetric oxygen binding
Baer et al performed this coordination analysis for their single-temperature study, but discriminated between \suldiox~binding through the two different oxygens. They concluded that there is asymmetric hydrogen bonding through the \suldiox~oxygens, with one binding more often than the other. This is supported by the findings here where all the double oxygen coordinations (i.e. ``OO'', ``SOO'', etc.) represent a much lower percentage of the coordinations than the single oxygen counterparts (i.e. ``O'', ``SO'', etc.). Furthermore, a triple-oxygen coordination (i.e. ``OOO'', ``SOOO'', etc.) is very rarely encountered. Three \suldiox~oxygen bonds only form if both \suldiox~oxygens are interacting with water hydrogens. Our finding that triple-oxygen coordinations rarely form complements Baer et al's conclusion about the assymetry in the oxygen interactions.

Having established the preference for an interaction through the \suldiox~sulfur atom, we look to the right side of Figure \ref{fig:bonding-coordinations} at the double-sulfur coordinations (i.e. ``SS'', ``SSO'', ``SSOO'', etc.). We see from the data that single-sulfur coordinations are overwhelmingly preferred over double-sulfur ones. Adding a third oxygen atom is also unfavorable as the ``OOO'' and ``SSOOO'' are represented less than 1\% of the trajectories, and the comparison between ``SOO'' to ``SOOO'' shows a very large decrease in occurences.

We can now form a picture of a typical \suldiox~molecule adsorbed to a water surface across both temperatures in this study. The \suldiox~will have at least one interaction to neighboring waters through the sulfur, and will then bond assymetrically through one of the oxygens either once or twice to water hydrogens. The \suldiox~oxygen bonds will form and break repeatedly throughout a trajectory, and overall the most dominant coordination will be the ``SO'' bonding arrangement.

@@

The binding behavior of the \suldiox~is altered by changing the temperature of the system, as evidenced in the shift in bonding coordination populations of Figure \ref{fig:bonding-coordinations} from cold to hot. In the cold temperature, the unbound, ``S'', and ``SO'' coordinations are more populated than in the hot systems. The increased temperature decreases the time spent in the unbound coordination, and causes all the coordinations to the right of ``SO'' in Figure \ref{fig:bonding-coordinations} to increase over the equivalent cold temperature coordination populations. We see that the cold \suldiox~spends nearly four times as much time unbound as the hot \suldiox, with most of the unbound population in the hot simulations shifting to coordinations with double-oxygen and double-sulfur bonds.

@@

During the course of each cold and hot simulation, the \suldiox~bonding coordination was determined and recorded for each timestep. From the coordination data we extract not only the populations of the various bonding coordinations, but also the frequencies of transitions between the different coordinations (i.e. the number of times each \suldiox~switched from one coordination type to another). With this data we have generated the directed graphs of Figure \ref{fig:coordination-transitions} depicting the cold and hot (Figure \ref{fig:coordination-transitions} A and B, respectively) bonding coordinations as circular colored nodes.\cite{Ellson2004,Gansner1999} The transitions between the coordinations are depicted as directed edges pointing in the direction of the transition from one coordination to another. The populations of the coordinations are depicted by both the node size and coloration (larger and darker red coordinations occur more frequently). Populations of the transitions between coordinations are depicted by arrow thickness, with thicker lines corresponding to more frequently occuring transitions. Additionally, the transition lines are numbered to the right of each line with the number of times each transition occured.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/coordination-transitions.png}
		\caption{The bonding coordinations of \suldiox~on a water surface rapidly change as bonds break and form throughout the MD trajectories. Depicted here is a graph of the bonding coordinations, shown as colored nodes of varying size. Larger and more darkly colored coordination nodes are those more often encountered during MD (see Figure \ref{fig:bonding-coordinations}). The directed edges between the nodes represent the number of times the coordination transition occured. Thicker lines correspond to a greater number of transitions between coordinations. The number of time a given transition occured is labeled to the right of the corresponding line.}
		\label{fig:coordination-transitions}
	\end{center}
\end{figure}

As expected for the more populated coordinations, there are more transitions between larger nodes in Figure \ref{fig:coordination-transitions} than transitions to less populated coordinations. However, some insights to the bonding process are made clearer from these graphs. In the cold system graph of Figure \ref{fig:coordination-transitions}A, we find that the majority of transitions are between the ``S-SO'' and ``SO-SOO'' nodes. The number of transitions within this ``S-SO-SOO'' grouping of coordinations is an order of magnitude larger than any other transition. This indicates that while the \suldiox~is bound in any of the three most populated bonding coordinations, it is actively binding and unbinding the oxygens to form the other two coordinations in this group. Clearly, the \suldiox~is rather active and constantly forming and breaking bonds with its oxygens.

In the graph of the hot system in Figure \ref{fig:coordination-transitions}B, the transition frequencies follow the same trend as in the cold system, increasing with adjacent node size. One very surprising result is in the transition from ``SOO-SOOO''. The transition frequency does not follow from the adjacent node sizes, as the ``SOOO'' node represents less than 5\% of the bonding coordinations. This is indicative of a very rapid cycle of forming and breaking of bonds to the second \suldiox~oxygen. As noted earlier, it is likely that ``SOO'' coordinated \suldiox, assymetrically binding twice through a single oxygen, is being pulled further into the water interface. It is likely more surrounded by waters, and in the hot system it can more easily form a brief third hydrogen bond to a water through the second \suldiox~oxygen. Because the triple-oxygen coordination is not as favorable, it quickly breaks the bond and the \suldiox~returns back to the ``SOO'' coordination.

@@

To verify if the ``O'' coordination forms from, and breaks quickly to the unbound coordination as is suggested by the transition frequency plots in Figure \ref{fig:coordination-transitions}, we plot the lifespans of the various coordinations in Figure \ref{fig:coordination-lifespans}. Each point in the plot represents a time during the simulation in which the \suldiox~formed the respective coordination. The vertical ``lifespan'' position is calculated directly from the amount of time spent in the given coordination before changing to another. Both cold (blue) and hot (red) simulation data are plotted. The data of Figure \ref{fig:coordination-lifespans} show that most coordination configurations last a very brief time, with the majority forming for under 0.5 ps. The three most populous coordinations, ``S'', ``SO'', ``SOO'' (as determined from Figure \ref{fig:bonding-coordinations} by percentage) in both temperatures have coordination lifetimes of up to 1 ps, in some instances lasting up to 1.5 ps. The brevity of lifespans overall speaks to the dynamic nature of the interface. The length of time in each coordination parallels the populations of the coordinations, and suggests an ordering of steady states among various bonding coordinations. The ``unbound'' configuration stands out as an anomaly amonst the lifespans of the other bonding coordinations. The few lifespans above 1.5 ps, up to 3.25 ps long, suggest a \suldiox~that not only unbinds from the water surface, but that also recedes far enough to avoid a quick rebinding and coordination change to ``S'' or ``O''. Those few long lived unbound data points indicate times when the \suldiox~is far from the water, residing in the gas phase until the necessary water rearrangement occurs and it is drawn back to the surface to rebind.

@@

Once the \suldiox~begins interacting with the water surface, the pathway leading back to the unbound coordination is not often traversed. As shown in Figure \ref{fig:coordination-transitions} the dominant coordination transitions occur between the cluster of ``S-SO-SOO'' coordinations. This suggests that the \suldiox~sulfur interaction to a water oxygen has a much longer lifespan than the oxygen bonding to water hydrogens. The difference between the ``S-SO-SOO'' coordinations is an addition or removal of oxygen bonds, and the frequent transitions between them show that the bonds to \suldiox~oxygens are quickly forming and breaking. For the \suldiox~sulfur interaction to break, the \suldiox~must enter a non-sulfur coordination (i.e. ``O'', ``OO'', unbound, etc.) or a coordination with more than a single sulfur interaction (i.e. ``SS'', ``SSO'', etc.). The transitions to coordinations that allow for breaking of the \suldiox~sulfur interactions, or switching the interaction to another water, are infrequent compared to those leading to an oxygen bond transition. Thus, the \suldiox~spends most of its time while bound to the surface waters breaking and forming hydrogen-bonds through its oxygens, and interacting with neighboring waters through a more persisten interaction via the \suldiox~sulfur atom.

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/so2-coordinations-percents-small.png}
		\caption{The \suldiox~bonding coordinations occur with different frequencies at the surface under hot and cold temperature conditions. Shown above is the distribution of bonding coordinations of the cold (blue) and hot (red) \suldiox~over the entire set of trajectories. The values are the percentage of MD timesteps spent in the given bonding coordination.}
		\label{fig:bonding-coordinations}
	\end{center}
\end{figure}

	Several conclusions about the bonding behavior of \suldiox~to surface waters stem from this distribution of coordinations. Clearly the cold \suldiox~spends more time than the hot \suldiox, 13\% versus 3\%, respectively, completely unbound from the surface waters. This does not necessarily imply a complete desorption into the gas phase, but only a brief sojourn away from the waters, with all interactions and bond lengths longer than the cutoff criteria used for the analysis. Furthermore, the most frequently occurring bonding coordinations are ``S'',``SO'', and ``SOO'', with ``SO'' being the most populated at both temperatures. Baer et al. also concluded that these three coordinations were the most frequent for a room temperature simulation, and specifically identified the ``SO'' and ``SOO'' as most common in their study.\cite{Baer2010}

@@

% Baer's assymetric oxygen binding
Baer et al performed this coordination analysis for their single-temperature study, but discriminated between \suldiox~binding through the two different oxygens. They concluded that there is asymmetric hydrogen bonding through the \suldiox~oxygens, with one binding more often than the other. This is supported by the findings here where all the double oxygen coordinations (i.e. ``OO'', ``SOO'', etc.) represent a much lower percentage of the coordinations than the single oxygen counterparts (i.e. ``O'', ``SO'', etc.). Furthermore, a triple-oxygen coordination (i.e. ``OOO'', ``SOOO'', etc.) is very rarely encountered. Three \suldiox~oxygen bonds only form if both \suldiox~oxygens are interacting with water hydrogens. Our finding that triple-oxygen coordinations rarely form complements Baer et al's conclusion about the asymmetry in the oxygen interactions.

Having established the preference for an interaction through the \suldiox~sulfur atom, we look to the right side of Figure \ref{fig:bonding-coordinations} at the double-sulfur coordinations (i.e. ``SS'', ``SSO'', ``SSOO'', etc.). We see from the data that single-sulfur coordinations are overwhelmingly preferred over double-sulfur ones. Adding a third oxygen atom is also unfavorable as the ``OOO'' and ``SSOOO'' represent less than 1\% of the trajectories, and the comparison between ``SOO'' to ``SOOO'' shows a very large decrease in occurrences.

We can now form a picture of a typical \suldiox~molecule adsorbed to a water surface across both temperatures in this study. The \suldiox~will have at least one interaction to neighboring waters through the sulfur, and will then bond asymmetrically through one of the oxygens either once or twice to water hydrogens. The \suldiox~oxygen bonds will form and break repeatedly throughout a trajectory, and overall the most dominant coordination will be the ``SO'' bonding arrangement.

@@

The binding behavior of the \suldiox~is altered by changing the temperature of the system, as evidenced in the shift in bonding coordination populations of Figure \ref{fig:bonding-coordinations} from cold to hot. In the cold temperature, the unbound, ``S'', and ``SO'' coordinations are more populated than in the hot systems. The increased temperature decreases the time spent in the unbound coordination, and causes all the coordinations to the right of ``SO'' in Figure \ref{fig:bonding-coordinations} to increase over the equivalent cold temperature populations. We see that the cold \suldiox~spends nearly four times as much time unbound as the hot \suldiox, with most of the unbound population in the hot simulations shifting to coordinations with double-oxygen and double-sulfur bonds.

@@

During the course of each cold and hot simulation, the \suldiox~bonding coordination was determined and recorded for each timestep. From the coordination data we extract not only the populations of the various bonding coordinations, but also the frequencies of transitions between the different coordinations (i.e. the number of times each \suldiox~switched from one coordination type to another). With this data we have generated the directed graphs of Figure \ref{fig:coordination-transitions} depicting the cold and hot (Figure \ref{fig:coordination-transitions} A and B, respectively) bonding coordinations as circular colored nodes.\cite{Ellson2004,Gansner1999} The transitions between the coordinations are depicted as directed edges pointing in the direction of the transition from one coordination to another. The populations of the coordinations are depicted by both the node size and coloration (larger and darker red coordinations occur more frequently). Populations of the transitions between coordinations are depicted by arrow thickness, with thicker lines corresponding to more frequently occurring transitions. Additionally, the transition lines are numbered to the right of each line with the number of times each transition occurred.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/coordinations/coordination-transitions.png}
		\caption{The bonding coordinations of \suldiox~on a water surface rapidly change as bonds break and form throughout the MD trajectories. Depicted here is a graph of the bonding coordinations, shown as colored nodes of varying size. Larger and more darkly colored coordination nodes are those more often encountered during MD (see Figure \ref{fig:bonding-coordinations}). The directed edges between the nodes represent the number of times the coordination transition occurred. Thicker lines correspond to a greater number of transitions between coordinations. The number of time a given transition occurred is labeled to the right of the corresponding line.}
		\label{fig:coordination-transitions}
	\end{center}
\end{figure}

As expected for the more populated coordinations, there are more transitions between larger nodes in Figure \ref{fig:coordination-transitions} than transitions to less populated coordinations. However, some insights to the bonding process are made clearer from these graphs. In the cold system graph of Figure \ref{fig:coordination-transitions}A, we find that the majority of transitions are between the ``S-SO'' and ``SO-SOO'' nodes. The number of transitions within this ``S-SO-SOO'' group of coordinations is an order of magnitude larger than any other transition. This indicates that while the \suldiox~is bound in any of the three most populated bonding coordinations, it is actively binding and unbinding the oxygens to form the other two coordinations in this group. Clearly, the \suldiox~is rather active and constantly forming and breaking bonds with its oxygens.

In the graph of the hot system in Figure \ref{fig:coordination-transitions}B, the transition frequencies follow the same trend as in the cold system, increasing with adjacent node size. One very surprising result is in the transition from ``SOO-SOOO''. The transition frequency does not follow from the adjacent node sizes, as the ``SOOO'' node represents less than 5\% of the bonding coordinations. This is indicative of a very rapid cycle of forming and breaking of bonds to the second \suldiox~oxygen. As noted earlier, it is likely that ``SOO'' coordinated \suldiox, asymmetrically binding twice through a single oxygen, is being pulled further into the water interface. It is likely more surrounded by waters, and in the hot system it can more easily form a brief third hydrogen bond to a water through the second \suldiox~oxygen. Because the triple-oxygen coordination is not as favorable, it quickly breaks the bond and the \suldiox~returns back to the ``SOO'' coordination.

@@

To verify if the ``O'' coordination forms from, and breaks quickly to the unbound coordination as is suggested by the transition frequency plots in Figure \ref{fig:coordination-transitions}, we plot the lifespans of the various coordinations in Figure \ref{fig:coordination-lifespans}. Each point in the plot represents a time during the simulation in which the \suldiox~formed the respective coordination. The vertical ``lifespan'' position is calculated directly from the amount of time spent in the given coordination before changing to another. Both cold (blue) and hot (red) simulation data are plotted. The data of Figure \ref{fig:coordination-lifespans} show that most coordination configurations last a very brief time, with the majority forming for under 0.5 ps. The three most populous coordinations, ``S'', ``SO'', ``SOO'' (as determined from Figure \ref{fig:bonding-coordinations} by percentage) in both temperatures have coordination lifetimes of up to 1 ps, in some instances lasting up to 1.5 ps. The brevity of lifespans overall speaks to the dynamic nature of the interface. The length of time in each coordination parallels the populations of the coordinations, and suggests an ordering of steady states among various bonding coordinations. The ``unbound'' configuration stands out as an anomaly amongst the lifespans of the other bonding coordinations. The few lifespans above 1.5 ps, up to 3.25 ps long, suggest a \suldiox~that not only unbinds from the water surface, but that also recedes far enough to avoid a quick rebinding and coordination change to ``S'' or ``O''. Those few long lived unbound data points indicate times when the \suldiox~is far from the water, residing in the gas phase until the necessary water rearrangement occurs and it is drawn back to the surface to rebind.

@@

Once the \suldiox~begins interacting with the water surface, the pathway leading back to the unbound coordination is not often traversed. As shown in Figure \ref{fig:coordination-transitions} the dominant coordination transitions occur between the ``S-SO-SOO'' group of coordinations. This suggests that the \suldiox~sulfur interaction to a water oxygen has a much longer lifespan than the oxygen bonding to water hydrogens. The difference between the ``S-SO-SOO'' coordinations is an addition or removal of oxygen bonds, and the frequent transitions between them show that the bonds to \suldiox~oxygens are quickly forming and breaking. For the \suldiox~sulfur interaction to break, the \suldiox~must enter a non-sulfur coordination (i.e. ``O'', ``OO'', unbound, etc.) or a coordination with more than a single sulfur interaction (i.e. ``SS'', ``SSO'', etc.). The transitions to coordinations that allow for breaking of the \suldiox~sulfur interactions, or switching the interaction to another water, are infrequent compared to those leading to an oxygen bond transition. Thus, the \suldiox~spends most of its time while bound to the surface waters breaking and forming hydrogen-bonds through its oxygens, and interacting with neighboring waters through a more persistent interaction via the \suldiox~sulfur atom.

### 2011-08-26 Cycle-Results.tex
New round of edits given out to others

Having examined the bonding coordinations and bonding behavior of \suldiox~with surface waters, we now turn to a secondary behavior of the hydrate structures that form around the surface-bound \suldiox~molecule. The simulation trajectory data was analyzed to determine the presence and characteristics of \suldiox~cyclic hydrate structures that form during MD, as posited earlier in the text and depicted in Figure \ref{fig:cyclic-structures}. Only the most commonly occurring subset of the cyclic structures were analyzed based on two selection criteria for determining formation of a cyclic structure: (1) The distances between atoms must match the same bonding/distance criteria as used for determining bonding coordinations. (2) The \suldiox~must be minimally in a bonding coordination of type ``SO'', meaning that the sulfur has at least one bonding interaction, and at least one hydrogen-bond must have formed with an oxygen to a neighboring water-hydrogen. As noted earlier in the discussion of the graph-finding routine and the BFS algorithm, the cyclic structures found represent the smallest cycles in which the \suldiox~is a member, based on order of discovery. The \suldiox~will be involved in other larger and more extended cyclic bonding structures beyond the first one discovered via the BFS. The larger and more extended cyclic structures involving more waters affect the behavior of the hydrogen-bonding network of the water surface. However, we focus here only on the smallest cycles involving the \suldiox~as they most affect the \suldiox~bonding and hydration.

@@

The plot in Figure \ref{fig:cyclic-breakdown} shows the distribution of how often the various types of cyclic hydrates were encountered at both cold (blue) and hot (red) temperatures. Each data point shows a percentage of the MD trajectories in which the \suldiox~was a member of a cyclic structure, for different numbers of cyclic waters (up to 4). The two tallest data points, left-most in the plot, show the overall time spent in all types of cyclic structures. Clearly the hot system \suldiox~spends more time in a cyclic structure than at the cold temperature. It is remarkable that the difference of the time spent in a cyclic structure between the two temperatures is 15\% (42\% cold, 57\% hot). The hot \suldiox~spends well over half of the simulated time bound as one of the hydrate cycles, and the cold \suldiox~spends just under half of the time as such. Thus, in addition to having earlier found the most likely bonding coordination during the simulated life of \suldiox, we have also found that the hydrates of the \suldiox~form cyclic structures for much of the time while bound to the water surface.

@@

The results for triple and quadruple-water structures show that larger hydrate cycles are favored at higher temperatures. Although the higher number of hydrating waters ($>$ 4) are not shown, those contribute minimally to the overall distribution. The majority of the cyclic hydrates are formed with three waters in the triple-water type. This hydrate type matches the bonding structure inferred from our previous experiments, and also one of the cluster types modeled by others.\cite{Tarbuck2005,Tarbuck2006,Baer2010} It was further found that of the triple-type hydrate cycles, the waters contributing to the cycles can be arranged in two ways that preserve the hydrogen-bonding between the molecules (described earlier and shown in Figure \ref{fig:type-3-varieties}). The triple-water type cycle results were broken down into contributions from the type-A and type-B triple-water structures. The two triple cycle structures are depicted on the right side of Figure \ref{fig:cyclic-breakdown}, along with the plots of their contributions to the overall distribution. It is notable that each temperature has a different dominant type of triple-water cyclic structure. The cold system forms more of the type-B, and the hotter system forms primarily triple type-A.

@@

We know from the transition frequency plots of Figure \ref{fig:coordination-transitions} that the bonding coordinations are switching frequently. The \suldiox~is likely forming and breaking bonds with waters extraneous to the cyclic hydrate structures (i.e. not directly involved in the bonds of the cycle). For the longer-lived cycles, the extraneous bonding to the \suldiox~may have little effect on the cyclic hydrate waters. However, any time the \suldiox~switches into an unbound, sulfur-only, or oxygen-only coordination (i.e. ``S'', ``SS'', ``O'', etc), the cyclic structure is necessarily broken. Because the majority of cyclic structures last only briefly ($<1$ ps), the active switching of \suldiox~bonding coordinations appears to break the cyclic structure. Figure \ref{fig:bonding-coordinations} shows that the sum of coordinations that necessarily break cyclic structures account for approximately 39\% and 24\% of the bonding coordinations in the cold and hot system, respectively. Consequently, the distribution of Figure \ref{fig:cyclic-breakdown} also indicates that there are more cycles formed in the hot system (approximately 16\% above the cold). Of the three most encountered bonding coordinations, the hot system shifts population from the ``S'' (a cycle-breaking coordination) to ``SO'' and ``SOO'' (coordinations that allow for bonding cycle formation through the \suldiox), compared to the cold system coordination distribution. The increased temperature appears to cause the \suldiox~to bond in such a way that is more conducive to the formation of cyclic structures. This may account for the slightly increased populations of the longer cycle lifespans in the hot system (greater than 4 ps in some cases) compared to the cold system in the cycle lifespan distribution of Figure \ref{fig:cycle-lifespans}.

>>>>

Having examined the bonding coordinations and bonding behavior of \suldiox~with surface waters, we now turn to a secondary behavior of the hydrate structures that form around the surface-bound \suldiox~molecule. The simulation trajectory data was analyzed to determine the presence and characteristics of \suldiox~cyclic hydrate structures that form during MD, as posited earlier in the text and depicted in Figure \ref{fig:cyclic-structures}. Only the most commonly occurring subset of the cyclic structures were analyzed based on two selection criteria for determining formation of a cyclic structure: (1) The distances between atoms must match the same bonding/distance criteria as used for determining bonding coordinations. (2) The \suldiox~must be minimally in a bonding coordination of type ``SO'', meaning that the sulfur has at least one bonding interaction, and at least one hydrogen-bond must have formed with an oxygen to a neighboring water-hydrogen. As noted earlier in the discussion of the graph-finding routine and the BFS algorithm, the cyclic structures found represent the smallest cycles in which the \suldiox~is a member, based on the search's order of cycle discovery. The \suldiox~will be involved in other larger and more extended cyclic bonding structures beyond the first one discovered via the BFS. The larger and more extended cyclic structures involving more waters affect the behavior of the hydrogen-bonding network of the water surface. However, we focus here only on the smallest cycles involving the \suldiox~as they most affect the \suldiox~bonding and hydration.

@@

The plot in Figure \ref{fig:cyclic-breakdown} shows the distribution of how often the various types of cyclic hydrates were encountered at both cold (blue) and hot (red) temperatures. Each data point shows a percentage of the MD trajectories in which the \suldiox~was a member of a cyclic structure, for different numbers of cyclic waters (up to 4). The two tallest data points, left-most in the plot, show the overall time spent in all types of cyclic structures. Clearly the hot system \suldiox~spends more time in a cyclic structure than at the cold temperature. It is remarkable that the difference of the times spent in a cyclic structure between the two temperatures is 15\% (42\% cold, 57\% hot). The hot \suldiox~spends well over half of the simulated time bound as one of the hydrate cycles, and the cold \suldiox~spends just under half of the time as such. Thus, in addition to having earlier found the most likely bonding coordination during the simulated life of \suldiox, we have also found that the hydrates of the \suldiox~form cyclic structures for much of the time while bound to the water surface.

@@

The results for triple and quadruple-water structures show that larger hydrate cycles are favored at higher temperatures. Although the higher number of hydrating waters ($>$ 4) are not shown, those contribute minimally to the overall distribution. The majority of the cyclic hydrates are formed with three waters in the triple-water type. This hydrate type matches the bonding structure inferred from our previous experiments, and also one of the cluster types modeled by others.\cite{Tarbuck2005,Tarbuck2006,Baer2010} It was further found that of the triple-type hydrate cycles, the waters contributing to the cycles can be arranged in two ways that preserve the hydrogen-bonding between the molecules (described earlier and shown in Figure \ref{fig:type-3-varieties}). The triple-water type cycle results were broken down into contributions from the type-A and type-B triple-water structures. The two triple cycle structures are depicted on the right side of Figure \ref{fig:cyclic-breakdown}, along with the plots of their contributions to the overall distribution. It is notable that each temperature has a different dominant type of triple-water cyclic structure. The cold system forms more of the type-B, and the hotter system forms primarily type-A.

@@

We know from the transition frequency plots of Figure \ref{fig:coordination-transitions} that the bonding coordinations are switching frequently. The \suldiox~is likely forming and breaking bonds with waters extraneous to the cyclic hydrate structures (i.e. not directly involved in the bonds of the cycle). For the longer-lived cycles, the extraneous bonding to the \suldiox~may have little effect on the cyclic hydrate waters. However, any time the \suldiox~switches into an unbound, sulfur-only, or oxygen-only coordination (i.e. ``S'', ``SS'', ``O'', etc), the cyclic structure is necessarily broken. Because the majority of cyclic structures last only briefly ($<1$ ps), the active switching of \suldiox~bonding coordinations appears to break the cyclic structure. Figure \ref{fig:bonding-coordinations} shows that the sum of coordinations that necessarily break cyclic structures account for approximately 39\% and 24\% of the bonding coordinations in the cold and hot system, respectively. Consequently, the distribution of Figure \ref{fig:cyclic-breakdown} also indicates that there are more cycles formed in the hot system (approximately 16\% above the cold). Of the three most encountered bonding coordinations, the hot system shifts population from the ``S'' (a cycle-breaking coordination) to ``SO'' and ``SOO'' (coordinations that allow for bonding cycle formation through the \suldiox). This is relative to the cold system coordination distribution that has equal ``S'' and ``SOO'' populations. The increased temperature appears to cause the \suldiox~to bond in a way that is more conducive to the formation of cyclic structures. This may account for the slightly increased populations of the longer cycle lifespans in the hot system (greater than 4 ps in some cases) compared to the cold system in the cycle lifespan distribution of Figure \ref{fig:cycle-lifespans}.
